---
title: "Mining u2/merki"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE,
  collapse = TRUE,
  eval = FALSE,
  error = TRUE,
  comment = "#>"
)
```

```{r}
library(fs)
library(omar)
library(lubridate)
library(staroddi)
library(tidyverse)
```

## Problem statement

Although the DST-recaptures have systematically been reported along with conventional recaptures in the MFRI database, the DST profile records (time, temperature, depth, ...) have not.

Fortunately, many of the DST profiles (.DAT files) have been stored in a common directory (/u2/merki) since the beginning of the century. The problem here though is that the space has been used both as a raw data storage space as well as processing space. Hence one may have multiple identical original files or some extracts of the those in different folders.

The objective here is:

* Map the space, for now only focusing on the .DAT files
* Design an algorithm that:
  * Copy the most original version of a .DAT file (earliest modification date, most number of records) and store it in a single directory space.
  
What is not (yet) considered here is:

* Retrieval of auxillary files or whole directories
* Uploading of missing DST-profiles into the central database

```{r tagdata}
con <- connect_mar()
ak <- c("ISL.ELDI.", "UTE.DUMMY", "ISL.MILLI.", "ISL.RAF.", 
        "ESKIFJORDUR", "ISL.GPS.", "ISL.MICRO.", "BIOPOL",
        "Hafro.Selur", "SL.EHJ", "Pit tag", "DST", "Pop-up",
        "RAF")
tgs <- 
  taggart(con) %>% 
  filter(audkenni %in% ak) %>% 
  collect(n = Inf)
```

## .DAT mapping

All headers of the .DAT files within the `/u2/merki` are first gathered


TODO:

* ...
* ...

Problem :

* "/u2/merki/gogn/Hrognkelsi/M14613/1M14613.DAT" has got the mdy format for `Date-time:`

This should be solvable - just need to check the format in the header file

```{r mapping}
files <-
  fs::dir_info("/u2/merki", recurse = TRUE, fail = FALSE, glob = "*.DAT") %>%
  mutate(path = as.character(path),
         file = basename(path),
         ID = 1:n())
# read all the files
header <- 
  map(files$path, read_dst_header, long = FALSE) %>% 
  bind_rows() %>% 
  janitor::clean_names()
header %>% glimpse()
header %>% 
  mutate(loc = str_locate(recorder, "[a-zA-Z]+")[,1],
         utgafa = str_sub(recorder, 1, loc-1),
         ak = stringr::str_extract(recorder, "[a-zA-Z]+") |> stringr::str_to_upper(),
         numerc = stringr::str_sub(recorder, loc + 1),
         numer = as.integer(numerc),
         utgafa = as.integer(utgafa)) %>% 
  group_by(recorder) %>% 
  mutate(n.recorder = n()) %>% 
  ungroup() %>% 
  arrange(ak, numer, utgafa, desc(n), modification_time) %>% 
  group_by(recorder) %>% 
  mutate(n.tmp = 1:n()) %>% 
  # identify profile that has mininum modification_time and maximum n
  mutate(use = ifelse(n == max(n) & 
                        modification_time == min(modification_time) &
                        date_time == min(date_time) &
                        n.tmp == min(n.tmp),
                      TRUE,
                      FALSE)) %>% 
  ungroup() %>% 
  select(-n.tmp)
```

Problem with algorithm, fix upstream:

```{r}
d %>% 
  filter(is.na(date_time)) %>% 
  glimpse()
# the files to check
d %>% 
  filter(is.na(date_time)) %>% 
  pull(path)
```

... for the time being, filter these out:
```{r}
d <- 
  d %>% 
  filter(!is.na(date_time))
```


## Selection of .DAT files to "move"

```{r}
# what does modification time vs change_time mean??
d %>% 
  select(recorder, date_time, modification_time, change_time, path) %>% 
  mutate(diff = difftime(change_time, modification_time, units = "days")) %>% 
  arrange(diff)
```

... filtering


```{r}
d.filtered <- 
  d %>% 
  select(recorder, audkenni, numer, utgafa, n, modification_time, everything()) %>% 
  arrange(audkenni, numer, utgafa, desc(n), modification_time) %>% 
  group_by(recorder) %>% 
  # filter by mininum modification_time and maximum n
  filter(n == max(n) & 
           modification_time == min(modification_time) &
           date_time == min(date_time)) %>% 
  # above things being equal, take the first slice
  #  could here think about prioritizing the directory the data is taken from
  slice(1) %>% 
  ungroup()
```

... we should here have unique recorder

```{r}
d.filtered %>% 
  group_by(recorder) %>% 
  mutate(n.unique = n()) %>% 
  ungroup() %>% 
  filter(n.unique > 1) %>% 
  nrow()
```

## Make a copy of above files

... how to preserve time

... check out file_link

```{r}
map(d.filtered$path, file_copy, "/u2/reikn/einarhj/tgs/DAT")
```

## Read in again, now from the new location

```{r}
files <-
  fs::dir_info("/u2/reikn/einarhj/tgs/DAT", recurse = TRUE, fail = FALSE, glob = "*.DAT") %>%
  mutate(path = as.character(path),
         file = basename(path),
         ID = 1:n())
# read all the files
res <- map(files$path, read_dst_header, FALSE)

d <- 
  bind_rows(res) %>% 
  janitor::clean_names() %>% 
  mutate(loc = stringr::str_locate(recorder, "[a-zA-Z]+")[,1],
         utgafa = str_sub(recorder, 1, loc-1),
         audkenni = stringr::str_extract(recorder, "[a-zA-Z]+") |> stringr::str_to_upper(),
         numerc = stringr::str_sub(recorder, loc + 1),
         numer = as.integer(numerc),
         utgafa = as.integer(utgafa)) %>% 
  group_by(recorder) %>% 
  mutate(n.recorder = n()) %>% 
  ungroup()
d %>% 
  filter(n.recorder > 1) %>% 
  nrow()
```

```{r}
library(omar)
con <- connect_mar()
ak <- c("ISL.ELDI.", "UTE.DUMMY", "ISL.MILLI.", "ISL.RAF.", 
        "ESKIFJORDUR", "ISL.GPS.", "ISL.MICRO.", "BIOPOL",
        "Hafro.Selur", "SL.EHJ", "Pit tag", "DST", "Pop-up",
        "RAF")
rec.dst <- 
  taggart(con) %>% 
  filter(audkenni %in% ak) %>% 
  collect(n = Inf)
```

... just the taggart bookkeeping:

```{r}
rec.dst %>% 
  mutate(recaptured = ifelse(!is.na(rdate), TRUE, FALSE),
         onrecord = ifelse(!is.na(dst_id), TRUE, FALSE)) %>% 
  count(rsid, audkenni, recaptured, onrecord) %>% 
  knitr::kable()
```

... join with the mined data:

```{r}
rec.dst %>% 
  mutate(recaptured = ifelse(!is.na(rdate), TRUE, FALSE),
         onrecord = ifelse(!is.na(dst_id), TRUE, FALSE)) %>% 
  full_join(d %>% 
              select(recorder) %>% 
              mutate(on.disk = TRUE),
            by = c("dst_id" = "recorder")) %>% 
  mutate(on.disk = replace_na(on.disk, FALSE)) %>% 
  count(rsid, audkenni, recaptured, onrecord, on.disk) %>% 
  knitr::kable()
```

... hmmmmm, 


## Lets focus on cod
